### 2016-05-20 paper/figures.tex
Added new figure

>>>>

\newcommand{\FigTLS}{
\begin{figure*}[ht]
    \centering
    \includegraphics[width=0.9\textwidth,clip]{figures/tls.pdf}
    \caption{\textbf{Miner--Target Interaction}\,--\, %
	A single round-trip is required for each attempt to solve the proof-of-work. The client
	computes the \texttt{client\_random} to commit to a given previous block and set of 
	transactions, and only provides the server the option to use Diffie-Hellman Ephemeral
	cipher-suites. The server then calculates a signature dependent on the 
	\texttt{client\_random} and verifiable by the certificate the server provides.
}
    \label{fig:tls-connection}
\end{figure*}
}
